{\normalsize Seminar: Formal Specification} \\[1ex] Security of Multithreaded Programs by Compilation\cite{Barthe07}

### 2012-01-28 paper/paper.tex
removed trailing whitespace
fixed citation

The idea is to 'track and regulate' \cite{Zdancewic04} where information flows to
prevent the leak of secret information. The ways on which the information flows
through the system are called channels. Channels that are not indented to transport
information are called covered channels\cite{Sabelfeld03}. These covered channels can
be classified into the following categories (in the following examples $h$ is a secret
variable and $l$ a variable that is plublic):

>>>>

The idea is to 'track and regulate' \cite{Zdancewic04} where information flows to
prevent the leak of secret information. The ways on which the information flows
through the system are called channels. Channels that are not indented to transport
information are called covered channels. These covered channels can
be classified into the following categories \cite{Sabelfeld03} (in the following examples $h$ is a secret
variable and $l$ a variable that is plublic):
